Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/evaluation.tex
Added hw configuration for decision procedures.
From reviewer 12:

> The hardware configuration should be specified (in Section 7.1)
> before discussing the runtimes (in Section 7.2)

In section 7.1, we discuss the implementation of the Lucy decision
procedures and runtime. In section 7.2, we evaluate the decision
procedures. In section 7.3, we evaluate the runtime.

At the beginning of section 7.3, we describe the hardware on which we
run the 7.3 experiments. We never described the hardware configuration
of the experiments in 7.2. I think the reviewer is telling us to add it.
This commit does

\subsection{Implementation}
Lucy includes an implementation of the interactive decision procedure described
in \algoref{InteractiveDecisionProcedure}, an implementation of a decision
procedure which checks criteria (1) - (4) from \thmref{LatticeProperty}, and an
implementation of the decision procedure described in
\algoref{ArbitraryStartInteractiveDecisionProcedure}. The decision procedures
are implemented in roughly 2,500 lines of Python. Users specify objects,
transactions, and invariants in a small Python DSL and interact with the
interactive decision procedures using an interactive Python console. We use
Z3~\cite{de2008z3} to implement our \invariantclosure{} decision procedure,
compiling an object and invariant into a formula that is satisfiable if and
only if the object is \emph{not} \invariantclosed{}. If the object is
\invariantclosed{}, then Z3 concludes that the formula is unsatisfiable.
Otherwise, if the object is not \invariantclosed{}, then Z3 produces a
counterexample witnessing the satisfiability of the formula.

@@

\subsection{Decision Procedures}
We now evaluate the practicality and efficiency of our decision procedure
prototypes. We begin by demonstrating the decision procedure on a handful of
simple, yet practical examples. We then discuss how our tool can be used to
analyze the TPC-C benchmark. A summary of these results is given in
\tabref{EvalTable}.

>>>>

\subsection{Implementation}
Lucy includes an implementation of the interactive decision procedure described
in \algoref{InteractiveDecisionProcedure}, an implementation of a decision
procedure which checks criteria (1) - (4) from \thmref{LatticeProperty}, and an
implementation of the decision procedure described in
\algoref{ArbitraryStartInteractiveDecisionProcedure}. The decision procedures
are implemented in roughly 2,500 lines of Python. Programmers specify objects,
transactions, and invariants in a small Python DSL and interact with the
interactive decision procedures using an interactive Python console. Note that
a programmer only has to run the decision procedures offline a single time to
check the \invariantconfluence{} of their distributed object. The decision
procedures do not have to be run online when transactions are being processed.

We use Z3~\cite{de2008z3} to implement our \invariantclosure{} decision procedure,
compiling an object and invariant into a formula that is satisfiable if and
only if the object is \emph{not} \invariantclosed{}. If the object is
\invariantclosed{}, then Z3 concludes that the formula is unsatisfiable.
Otherwise, if the object is not \invariantclosed{}, then Z3 produces a
counterexample witnessing the satisfiability of the formula.

@@

\subsection{Decision Procedures}
We now evaluate the practicality and efficiency of our decision procedure
prototypes. We begin by demonstrating the decision procedure on a handful of
simple, yet practical examples. We then discuss how our tool can be used to
analyze the TPC-C benchmark. All decision procedures were run on a MacBook Pro
laptop with a 3.5 GHz Intel Core i7 processor and 16 GB of RAM. A summary of
these results is given in \tabref{EvalTable}.
